Think deep for reef resilience

### 2025-08-07 paper/paper_draft.qmd
Fix error in ecs plot reference and adjust DHW figure units label
Table formatting and tweaks

| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
|----|----|----|----|
| EC-Earth3-Veg | 4.31 | High | Supplementary |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Supplementary |
| ACCESS-CM2 | 4.72 | High | Main text |
| GFDL-CM4 | 2.9 | Low | Supplementary |
| NorESM2-MM | 2.5 | Low | Supplementary |

: Table 1: Information for each GCM used in this investigation including ECS value,
interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@fig-ecs].
ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
results are displayed in the main text. ECS value sources: .

>>>>

| Global Climate Model source | ECS value (°C) | Interpreted relative severity | Individual results displayed |
|-----------------------|-----------------------|-----------------------|-----------------------|
| EC-Earth3-Veg | 4.31 | High | Supplementary |
| ACCESS-CM2 | 4.72 | High | Supplementary |
| ACCESS-ESM1-5 | 3.87 | Intermediate | Main text |
| GFDL-CM4 | 2.9 | Low | Supplementary |
| NorESM2-MM | 2.5 | Low | Supplementary |

: Table 1: Information for each GCM used in this investigation including ECS value,
interpreted relative severity and where results are individual GCM results are displayed. GCMs in context with assessed plausible ranges of ECS values are displayed in [@sfig-ecs].
ACCESS-ESM1-5 is taken as an intermediate model based on the range of ECS values, thus
results are displayed in the main text. ECS value sources: .
